Modeling mental simulation: a computational analysis of mental rotation

### 2014-01-29 man/cogsci-2014/cogsci-2014.tex
Small changes in analysis section

\TODO{put correlations in figures}

@@

Out of the 247 participants, 200 (81\%) were included in our
analyses. Of the rest, we excluded 10 (4\%) because of an experimental
error, 6 (2.4\%) because they had already compelted a previous version
of the experiment, and 31 (12.6\%) because they failed a comprehension
check. A participant was marked as passing the comprehension check if
they answered at least 85\% of ``easy'' trials correctly. ``Easy''
trials were defined to be those for which the presented shapes
differed by a rotation of no more than 20 degrees.

@@

For analyses of response time, confidence intervals were computed
using a bootstrap analysis (sampling with replacement) with 1000
bootstrap samples. Response times were only only considered for
correct responses.

For analyses of accuracy, confidence intervals were
computed from a binomial proportion with a Jeffrey's beta prior.  For
correlations, we performed a bootstrap analysis (sampling with
replacement) over Spearman correlations using 10000 bootstrap samples.

To test if participants or a model was above chance on a particular
stimulus, we used the same posterior and checked whether $p>0.05$ for
the 50\% mark.

>>>>

@@

Out of the 247 participants, 200 (81\%) were included in our
analyses. Of the rest, we excluded 10 (4\%) because of an experimental
error, 6 (2.4\%) because they had already compelted a previous version
of the experiment, and 31 (12.6\%) because they failed a comprehension
check. A participant was marked as passing the comprehension check if
they answered at least 85\% of ``easy'' trials correctly. ``Easy''
trials were defined to be those for which the presented shapes
differed by a rotation of no more than 20 degrees. \TODO{mention
  excluding trials where people took a really long time to respond}

@@

For analyses of response time, confidence intervals were computed
using a bootstrap analysis (sampling with replacement) with 1000
bootstrap samples. Response times were only only considered for
correct responses.  We also used a bootstrap analysis (with 10000
bootstrap samples) to compute the confidence intervals for both
Spearman ($r_s$) and Pearson ($r$) correlations.

For analyses of accuracy, confidence intervals were computed from a
binomial proportion with a Jeffrey's beta prior.  To test if
participants or a model was above chance on a particular stimulus, we
used the same binomial proportion, and simply tested whether $p>0.05$
for the 50\% mark.
